High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2015-11-19 rmarkdown/chip_exo_paper.Rnw
Added plots on enrichment and strand imbalance

In order to asses the strand imbalance we create the following
visualization in figure \ref{fig:strand}. A) presents the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by fragments of both
strand or only one. Roughly speaking in a lower quality dataset there
is going to be a higher amount of single stranded-regions. To evaluate
this statement, for each replicate of the FoxA1 dataset from
\cite{exoillumina}, we divided the regions considered by the QC
pipeline into two sets by reviewing if they overlap any of the
sample's peaks and then calculate the Kolmogorov-Smirnov test.

>>>>

<<fsr,include = FALSE,eval = TRUE,echo = FALSE>>=

  de <- 100

pval <- list()
pval[[1]] <- 0.1039
pval[[2]] <- 0.0064
pval[[3]] <- 0.0871

In order to asses the strand imbalance we create the following
visualization in figure \ref{fig:strand}. A) presents the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by fragments of both
strand or only one. Roughly speaking in a lower quality dataset there
is going to be a higher amount of single stranded-regions. To evaluate
this statement, for each replicate of the FoxA1 dataset from
\cite{exoillumina}, we divided the regions formed by at least
\Sexpr{de} fragments into into the ones that overlap with any of the
sample's peaks. The p.value for ERR36935 is \Sexpr{pval[[1]]}, for
ERR336942 is \Sexpr{pval[[2]]} and for ERR336956 is \Sexpr{pval[[3]]}.
